### 2016-04-15 thesis/thesis.tex
organised the directory structure
added a bit of plan in my thesis; added few more file types in .gitignore; added reference style file

% Preamble:
\usepackage[T1]{fontenc}       % package for specifying output font encoding
\usepackage[utf8]{inputenc}    % package for specifying input font encoding
\usepackage{graphicx}          % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}          % package for Times New Roman font
\usepackage{setspace}          % package for setting line space

@@

@@

\include{./title}

@@

\include{./abstract}

\include{./acknowledgement}

@@

\include{./intro}

\include{./methods}

\include{./results}

\include{./discussion}

>>>>

% Preamble:
\usepackage[T1]{fontenc}                     % package for specifying output font encoding
\usepackage[utf8]{inputenc}                  % package for specifying input font encoding
\usepackage{natbib}                          % package for reference management
\usepackage{graphicx}                        % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                        % package for Times New Roman font
\usepackage{chngcntr}                        % package for making continuous figure numbering, instead of section-based numbering
\usepackage{setspace}                        % package for setting line space (used in title page)
\usepackage[hidelinks, colorlinks]{hyperref} % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                    % package for tweaking the chapter/section/subsection titles format

% Set up the hyperlinks - hange the colour of the links to blue:
\hypersetup{allcolors=blue}

% change figure numbering from section-based to continuous:
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}

@@

% Change the title of bibliography to references:
\renewcommand{\bibname}{References}

@@

\include{./misc/title}

@@

\include{./misc/abstract}

\include{./misc/acknowledgement}

@@

\include{./intro/intro}

\include{./methods/methods}

\include{./results/results}

\include{./results/results2}

\include{./discussion/discussion}

% Use the reference style specified in BiocRefStyle.bst:
\bibliographystyle{BiocRefStyle}

% Print out the bibliography:
\bibliography{MSc}
